Software for Automated Theorem Proving Based on the Calculus of Positively Constructed Formulas\thanks{Research is supported by Russian Foundation of Basic Research, grant No 14-01-31449~mol\_a.}

### 2015-09-06 paper.tex
Spell check continued. Release.

Prover showed good performace for problems, whose formalization in the PCF language contains large conjuncts (type conditions).

@@

The abstract syntax tree is passed to translation component that imports the tree, translates the FOF or CNF, performs some reduction of subformulas by applying a set of rules, converts the formulas into the PCF language. Translator also performs additional trivial reduction of the PCFs, renames the quantifier variables, and, at the last step, outputs the conversion result as textual representation of the problem in the language of the prover.

@@

%=============================
\subsubsection{Lazy concretion.}
Lazy concretion strategy allows one in most cases to find a substitution for an unconfined variable in acceptable time as compared to the sequential enumeration of Herbrand universum. The constraints are the most valuable part of this strategy, which allow to decrease the number of steps of logical inference in comparison to the unconstrained strategy. The decrease of the number of steps leads to a decrease of the problem solving time. Application of the UHE constraint~1 (limiting depth of instantiation) is the best way of the inference time reduction in the case when a formula has questions with disjunctive branching and the constraint~2 (storing UHE expression) in case if the formula contains no questions without disjunctive branching.

@@

%===========================
\subsubsection{Parallel stratgies.}
The important quality of parallel schemes of algorithms is their scalability, i.e., the performance improvement respect to increase of the number of computational nodes (CNs). That’s why the main characteristic of the prover productivity is not the time of execution of the program, but the ratio of program execution time in parallel mode on a given number of CNs to the program execution time on a single CN. The ratio has been evaluated for various number of CNs.

>>>>

Prover showed good performance for problems, whose formalization in the PCF language contains large conjuncts (type conditions).

@@

The abstract syntax tree is passed to translation component that imports the tree, translates the FOF or CNF (conjunctive normal form), performs some reduction of subformulas by applying a set of rules, converts the formulas into the PCF language. Translator also performs additional trivial reduction of the PCFs, renames the quantifier variables, and, at the last step, outputs the conversion result as textual representation of the problem in the language of the prover.

@@

%=============================
\subsubsection{Lazy concretion.}
Lazy concretion strategy allows one in most cases to find a substitution for an unconfined variable in acceptable time as compared to the sequential enumeration of Herbrand universe. The constraints are the most valuable part of this strategy, which allow to decrease the number of steps of logical inference in comparison to the unconstrained strategy. The decrease of the number of steps leads to a decrease of the problem solving time. Application of the UHE constraint~1 (limiting depth of instantiation) is the best way of the inference time reduction in the case when a formula has questions with disjunctive branching and the constraint~2 (storing UHE expression) in case if the formula contains no questions without disjunctive branching.

@@

%===========================
\subsubsection{Parallel strategies.}
The important quality of parallel schemes of algorithms is their scaleability, i.e., the performance improvement respect to increase of the number of computational nodes (CNs). That’s why the main characteristic of the prover productivity is not the time of execution of the program, but the ratio of program execution time in parallel mode on a given number of CNs to the program execution time on a single CN. The ratio has been evaluated for various number of CNs.
